Borel regularity for ODEs and Thimble Integrals

### 2023-11-24 exp-resurgence.tex
Moved some part of the intro into the historical section Removed appendix on the geometry of thimbles and create a new doc.

Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization. We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged. In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
\subsubsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite{watson} that a function $F$ that vanishes at infinity is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around infinity (see Definition~\ref{def:unif-gevrey-asymp}).

%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular. Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity. Hence $\Phi$ is Borel-regularizable. In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$. In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity. 
\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
The idea of Borel regularity can help us understand why Borel summation is so effective in some situations. Roughly speaking, Borel summation works well for problems that admit solutions in terms of Laplace transform.

@@

The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag. 105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.

\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}

\begin{equation*}
I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
\end{equation*}
where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.  
\end{enumerate}

These two problems are closely linked. By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.

@@

Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations. On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain. 
\subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).

@@

Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
\begin{equation}\label{formal solution}
\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
\end{equation}
where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$. Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}). Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form 
\begin{equation}
\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
\end{equation}
labeled by the roots of $P$. This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}). In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$. 
At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$. Our main result says they are actually proportional, hence proving Borel summation works. 
\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.  
\end{theorem}
In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

\begin{remark}
The theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$ (namely, drawing the red arrow of the diagram). This ensures that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE. However, the approach of Borel regularity is different as it is based on the analytic solution in the position domain. 
\end{remark}
%\color{gray}
%\begin{itemize}
%\item Can we see there exists a distinguished basis in a purely analytic way? YES. %%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
%\end{itemize}
%\begin{itemize}
%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$. (proof based on existence theorem \ref{frac_int_exist})
%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially. Then this is the only solution that can be expressed as a Laplace transform. [Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]

@@

Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself.

\textcolor{red}{These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}. In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence,Howls}.}

We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. 
For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}}

\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}
Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
\begin{theorem}[see Theorem \ref{thm:maxim-dim}]\label{thm:maxim}
    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
\begin{multline}\label{eqn:formula}
\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{enumerate}
\end{theorem}

The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
\[
\begin{tikzcd}
{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
& & &\\
\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
\end{tikzcd}
\]
On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$. In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}. 
On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series. Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$. At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same. In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
%% the following remark has been moved to Section of the proof
%\begin{remark}\label{rmk:Pham formula}
%    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$. When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as 
%    \begin{equation}\label{eqn:Pham}
 %       (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
 %   \end{equation}
%for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
 %  \begin{equation*}
  %     \delta^{-\alpha}:=\begin{cases}
   %        \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
    %       & \\
     %      \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
      % \end{cases}
   %\end{equation*}
%In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case. We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one. 
%\end{remark}
%     
\subsubsection{Other results}
%
As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}). Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the position domain. We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}). Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the \textcolor{red}{spatial/frequency?} domain.

@@

Among the examples we study, some of them have been discussed many times, using different approaches and conventions. We try to give an idea of how all these different treatments fit together. For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}). The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}). Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.

@@

\section{Geometry of thimble integrals}\label{apx:geometry_thimble_integrals}

>>>>

Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization. We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged. In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.

\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
The idea of Borel regularity can help us understand why Borel summation is so effective in some situations. Roughly speaking, Borel summation works well for problems that admit solutions in terms of Laplace transform.

@@

The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag. 105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
%
\begin{equation*}
I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
\end{equation*}
where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.  
\end{enumerate}
These two problems are closely linked. By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.

@@

Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations. On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain. 
\subsubsection{Why does Borel summation work for solutions of level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).

@@

Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
\begin{equation}\label{formal solution}
\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
\end{equation}
where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$. Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame. \textcolor{orange}{Add that the formal series is $1$-Gevrey.}
\color{gray}
Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}). Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).\color{black} Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form 
\begin{equation}
\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
\end{equation}
labeled by the roots of $P$. This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}). In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$. 
At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$. Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.
\color{Maroon}
\begin{theorem}
For each root $\alpha$ of $P$,
\end{theorem}
\color{black}
\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}. \textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
\end{theorem}
In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

%\color{gray}
%\begin{itemize}
%\item Can we see there exists a distinguished basis in a purely analytic way? YES. %%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
%\end{itemize}
%\begin{itemize}
%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$. (proof based on existence theorem \ref{frac_int_exist})
%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially. Then this is the only solution that can be expressed as a Laplace transform. [Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]

@@

Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself. We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. 
For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}}

\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}
Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
\begin{theorem}[see Theorem \ref{thm:maxim-dim}]\label{thm:maxim}
    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
\begin{multline}\label{eqn:formula}
\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{enumerate}
\end{theorem}
The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
\[
\begin{tikzcd}
{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
& & &\\
\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
\end{tikzcd}
\]
On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$. In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}. 
On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series. Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$. At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same. In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
%% the following remark has been moved to Section of the proof
%\begin{remark}\label{rmk:Pham formula}
%    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$. When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as 
%    \begin{equation}\label{eqn:Pham}
 %       (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
 %   \end{equation}
%for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
 %  \begin{equation*}
  %     \delta^{-\alpha}:=\begin{cases}
   %        \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
    %       & \\
     %      \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
      % \end{cases}
   %\end{equation*}
%In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case. We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one. 
%\end{remark}
\subsubsection{Other results}
As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}). Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the position domain. We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}).

@@

Among the examples we study, some of them have been discussed many times, using different approaches and conventions. We try to give an idea of how all these different treatments fit together. For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}). \textcolor{red}{The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).} Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.

@@

\section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}
\textcolor{red}{Shall we review the content of \cite{reg-sing-volterra}?}
